\section{ Research Interests }
\textbf{Method:} Robustness, Generalization, Trustworthy Machine Learning, Multimodal learning, Explainable AI.
\textbf{Applications:} Joint modeling of medical images (chest-X-rays or 2D mammograms) and reports for lung diseases (e.g., pneumonia) and breast cancer predictions.

\section{ Education }
    \cventry{Jan 2023 -- Dec 2026 (Expected)}%
      {Doctor of Philosophy, Electrical Engineering}%
      {Boston University}%
      {Boston, Massachusetts, USA}%
      {}%
      {
        \textit{Thesis}: \textbf{Interpretable Medical AI with Vision-Language Alignment}
        \\
        \textit{Advisor(s)}:
        {\href{https://www.batman-lab.com/}
        { \textbf{\textcolor{blue}{Dr. Kayhan Batmanghelich}}}}
        \\
        \textit{Committee}:
        {\href{https://people.bu.edu/bkulis/}{\textbf{\textcolor{blue}{Dr. Brian Kulis}}}},
        {\href{https://sites.bu.edu/depend/people/}{\textbf{\textcolor{blue}{Dr. Wenchao Li}}}},
        {\href{https://www.bu.edu/hic/profile/clare-poynton/}{\textbf{\textcolor{blue}{Dr. Clare Poynton}}}}
      }

    \cventry{Aug 2021 -- Dec 2022}%
      {Doctor of Philosophy, Intelligent Systems}%
      {University of Pittsburgh \emph{(Transferred to BU)}}%
      {Pittsburgh, Pennsylvania, USA}%
      {}%
      {
        \textit{Advisor(s)}:
        {\href{https://www.batman-lab.com/}
        { \textbf{\textcolor{blue}{Dr. Kayhan Batmanghelich}}}}
      }

    \cventry{Aug 2019 -- May 2021}%
      {Master of Science, Computer Science}%
      {University of Florida}%
      {Gainesville, Florida, USA}%
      {\textbf{3.88/4.00}}%
      {}%
      {
        \textit{Advisor}: {\href{https://epidemiology.phhp.ufl.edu/disl/}
        { \textbf{\textcolor{blue}{Dr. Mattia Prosperi}}}}
      }
      
    \cventry{Aug 2008 -- May 2012}%
      {Bachelor of Technology, Computer Science}%
      {Institute of Engineering and Management}%
      {Kolkata, West Bengal, India}%
      {\textbf{3.6/4.00}}%
      {}%
