\section{ Industry Experience}
\subsection{United Imaging Intelligence (UII-America)}
    \cventry{May 2026 -- Aug 2026}%
      {UII-Computer Vision. Mentor: 
      {\href{https://wuziyan.com/}
        {\textbf{\textcolor{blue}{Dr. Ziyan Wu}}}}}%
      {Research Scientist Intern}%
      {Boston, MA, USA}%
      {}%
      {}
      \vspace{-1.2em}
      {
        \begin{itemize}[itemsep=0pt, parsep=0pt]
        \item Developing Video LLM for surgical video understanding.
        \end{itemize}
      }
      
    \subsection{Amazon}
    \cventry{May 2025 -- Aug 2025}%
      {AWS Optimus. Mentor: 
      {\href{https://ankanbansal.com/}
        {\textbf{\textcolor{blue}{Dr. Ankan Bansal}}}}}%
      {Applied Scientist Intern}%
      {Pasadena, California, USA}%
      {}%
      {}
      \vspace{-1.2em}
      {
        \begin{itemize}[itemsep=0pt, parsep=0pt]
        \item Developed an algorithm to detect and mitigate biases in the multi-modal LLM coding agents.
        \end{itemize}
      }
    \subsection{Amazon}
    \cventry{Jun 2024 -- Sep 2024}%
      {AWS, Security Analytics and AI Research (SAAR). Mentor: 
      {\href{https://scholar.google.com/citations?user=fsrkabwAAAAJ&hl=en}
        {\textbf{\textcolor{blue}{Dr. Mikhail Kuznetsov}}}}}%
      {Applied Scientist Intern}%
      {NYC, New York, USA}%
      {}%
      {}
      \vspace{-1.2em}
      {
        \begin{itemize}[itemsep=0pt, parsep=0pt]
        \item Developed a framework to learn robust representations to fix systematic errors in pre-trained self-supervised models for tabular data. Publication at \textbf{TRL@NeurIPS 2024}.
        \end{itemize}
      }
    \subsection{Lexmark International India Pvt Ltd}
    \cventry{Oct 2016 -- Jul 2019}%
      {}%
      {Software Engineering Professional II}%
      {Kolkata, India}%
      {}%
      {}
      \vspace{-1.5em}
      {
        \begin{itemize}[itemsep=0pt, parsep=0pt]
        \item Developed the ISP component of the product \href{https://infoserve.lexmark.com/ids/idv/video.aspx?category=All&productCode=PUBLISHING_PLATFORM_FOR_RETAIL&topic=v54408848&vId=PPR%2fLexmark-PPR-ISP-Overview-video&ar=16%3a9&l1=1&l2=1&sh=969&sw=1920&loc=en_US}
        {\textbf{\textcolor{blue}{Publishing Platform for Retail (PPR)}}}.
        % \item Worked on the Lexmark Digital Media Platform, a multi-tenant enterprise video content management platform hosted in Amazon Web Services.
        \end{itemize}
      }
    
  
    \subsection{Cognizant Technology Solutions India Pvt Ltd}
    \cventry{Mar 2013 -- Sep 2016}%
      {}%
      {Associate, Projects}%
      {Kolkata, India}%
      {}%
      {}
      \vspace{-1.0em}
      {
        \begin{itemize}
        \item Developed \textbf{WCF} web services in the Contract First Approach using Service Oriented Architecture.
        % \item Trained C\# to new recruits in Cognizant Academy.
        \end{itemize}
      }
  
    % Worked as a senior developer to develop WCF web services in the Contract First Approach to provide a secure communication channel between the different In-house applications using Service Oriented Architecture (SOA), C# .Net 4.5, Oracle Client 11g. Trained C\# to new recruits in Cognizant Academy.