\documentclass[10pt,letterpaper]{article}
\usepackage{academic_cv}

\hypersetup{pdftitle={Shantanu Ghosh Academic CV}}

\begin{document}

\cvname{Shantanu Ghosh}
\cvcontact{
Ph.D. Candidate, Electrical and Computer Engineering, Boston University \\
Email: \href{mailto:shawn24@bu.edu}{shawn24@bu.edu} \sep
Website: \href{https://shantanu-ai.github.io/}{shantanu-ai.github.io} \sep
Google Scholar: \href{https://scholar.google.com/citations?user=U_s5k_oAAAAJ\&hl=en}{profile} \sep
GitHub: \href{https://github.com/shantanu-ai}{shantanu-ai} \sep
LinkedIn: \href{https://www.linkedin.com/in/shantanuai/}{shantanuai}
}

\cvsection{Research Interests}
Trustworthy machine learning; robustness and generalization; multimodal learning; explainable artificial intelligence; vision-language models for medical imaging; radiology report generation; breast cancer risk prediction and chest radiograph analysis.

\cvsection{Education}
\cvdated{Boston University}{Jan 2023--Dec 2026 expected}{
Ph.D., Electrical Engineering. Thesis: \textit{Interpretable Medical AI with Vision-Language Alignment}. Advisor: \href{https://www.batman-lab.com/}{Kayhan Batmanghelich}. Committee: \href{https://people.bu.edu/bkulis/}{Brian Kulis}, \href{https://sites.bu.edu/depend/people/}{Wenchao Li}, \href{https://www.bu.edu/hic/profile/clare-poynton/}{Clare Poynton}.
}
\cvdated{University of Pittsburgh}{Aug 2021--Dec 2022}{
Ph.D. student, Intelligent Systems Program. Transferred to Boston University following advisor move.
}
\cvdated{University of Florida}{Aug 2019--May 2021}{
M.S., Computer Science. GPA: 3.88/4.00. Advisor: \href{https://epidemiology.phhp.ufl.edu/disl/}{Mattia Prosperi}.
}
\cvdated{Institute of Engineering and Management}{Aug 2008--May 2012}{
B.Tech., Computer Science. Kolkata, India.
}

\cvsection{Academic Appointments and Research Experience}
\cvdated{Graduate Research Assistant, Boston University}{Jan 2023--present}{
Advisor: \href{https://www.batman-lab.com/}{Kayhan Batmanghelich}; clinical collaborator: \href{https://www.bumc.bu.edu/camed/profile/clare-poynton/}{Clare Poynton}.
\begin{cvitems}
\item Developed LADDER, a language-driven slice discovery and error rectification method for vision classifiers; accepted at ACL 2025 Findings.
\item Developed Mammo-CLIP, a vision-language foundation model for 2D mammography; accepted at MICCAI 2024 as an early accept paper.
\item Applied mixtures of interpretable models for efficient transfer learning in chest radiograph classification; accepted at MICCAI 2023 as an early accept paper.
\end{cvitems}
}
\cvdated{Graduate Student Researcher, University of Pittsburgh}{Aug 2021--Dec 2022}{
Advisor: \href{https://www.batman-lab.com/}{Kayhan Batmanghelich}; collaborator: \href{https://forougha.github.io/}{Forough Arabshahi}.
\begin{cvitems}
\item Developed an iterative algorithm to extract mixtures of interpretable models from black-box classifiers using human-understandable concepts and first-order-logic explanations; accepted at ICML 2023.
\end{cvitems}
}
\cvdated{Graduate Research Assistant, University of Florida}{Jan 2020--Jul 2021}{
Advisors: \href{https://www.cise.ufl.edu/~butler/}{Kevin Butler}, \href{https://scholar.google.com/citations?user=ysr--voAAAAJ\&hl=en}{Jiang Bian}, and \href{https://epidemiology.phhp.ufl.edu/profile/prosperi-mattia/}{Mattia Prosperi}.
\begin{cvitems}
\item Developed DPN-SA, PSSAM-GAN, and DR-VIDAL for propensity score estimation, counterfactual prediction, and treatment-effect estimation.
\end{cvitems}
}

\cvsection{Industry Experience}
\cvdated{United Imaging Intelligence (UII-America)}{May 2026--Aug 2026}{
Research Scientist Intern, UII Computer Vision. Mentor: \href{https://wuziyan.com/}{Ziyan Wu}. Developing video LLMs for surgical video understanding.
}
\cvdated{Amazon Web Services, Optimus Team}{May 2025--Aug 2025}{
Applied Scientist Intern. Mentor: \href{https://ankanbansal.com/}{Ankan Bansal}. Developed methods to detect and mitigate biases in multimodal LLM coding agents.
}
\cvdated{Amazon Web Services, Security Analytics and AI Research}{Jun 2024--Sep 2024}{
Applied Scientist Intern. Mentor: \href{https://scholar.google.com/citations?user=fsrkabwAAAAJ\&hl=en}{Mikhail Kuznetsov}. Developed robust representation learning methods for systematic-error mitigation in tabular self-supervised models; publication at TRL@NeurIPS 2024.
}
\cvdated{Lexmark International India Pvt. Ltd.}{Oct 2016--Jul 2019}{
Software Engineering Professional II. Developed the ISP component of \href{https://infoserve.lexmark.com/ids/idv/video.aspx?category=All\&productCode=PUBLISHING_PLATFORM_FOR_RETAIL\&topic=v54408848\&vId=PPR\%2fLexmark-PPR-ISP-Overview-video\&ar=16\%3a9\&l1=1\&l2=1\&sh=969\&sw=1920\&loc=en_US}{Publishing Platform for Retail}.
}
\cvdated{Cognizant Technology Solutions India Pvt. Ltd.}{Mar 2013--Sep 2016}{
Associate, Projects. Developed WCF web services using a contract-first service-oriented architecture.
}

\cvsection{Publications}
\cvsubsection{Preprints}
\begin{cvitems}
\cvpub{Mammo-FM: Breast-specific foundational model for Integrated Mammographic Diagnosis, Prognosis, and Reporting}{\textbf{Shantanu Ghosh}, Vedant Parthesh Joshi, Rayan Syed, Aya Kassem, Abhishek Varshney, Payel Basak, Judy Wawira Gichoya, Hari M. Trivedi, Imon Banerjee, Clare B. Poynton, Shyam Visweswaran, Kayhan Batmanghelich}{arXiv}{2026.}{\cvlink{https://www.arxiv.org/pdf/2512.00198}{Paper}}
\end{cvitems}

\cvsubsection{Conference Proceedings}
\begin{cvitems}
\cvpub{MedSyn2: Flexible Control of 3D CT Generation via Text and Semantically-Defined Segmentation Prompts}{Weicheng Dai, Chenyu Wang, Binxu Li, \textbf{Shantanu Ghosh}, Afrooz Zandifar, Christina LeBedis, Kayhan Batmanghelich}{European Conference on Computer Vision (ECCV)}{2026.}{\cvlink{https://arxiv.org/abs/2606.00967}{Paper}}
\cvpub{PhyDiCT: Plug-and-Play CT Reconstruction from Sparse X-Rays via Differentiable Rendering and Strong Priors}{Weicheng Dai, \textbf{Shantanu Ghosh}, Kayhan Batmanghelich}{International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI)}{2026.}{}
\cvpub{LADDER: Language-Driven Slice Discovery and Error Rectification in Vision Classifiers}{\textbf{Shantanu Ghosh}, Rayan Syed, Chenyu Wang, Vaibhav Choudhary, Binxu Li, Clare B. Poynton, Shyam Visweswaran, Kayhan Batmanghelich}{Findings of the Association for Computational Linguistics (ACL)}{2025.}{\cvlink{https://shantanu-ai.github.io/projects/ACL-2025-Ladder/index.html}{Project} \cvlink{https://aclanthology.org/2025.findings-acl.1177/}{Paper} \cvlink{https://github.com/batmanlab/Ladder}{Code}}
\cvpub{Semantic Consistency-Based Uncertainty Quantification for Factuality in Radiology Report Generation}{Chenyu Wang, Weichao Zhou, \textbf{Shantanu Ghosh}, Kayhan Batmanghelich, Wenchao Li}{Findings of the Association for Computational Linguistics: NAACL}{2025.}{\cvlink{https://arxiv.org/pdf/2412.04606}{Paper} \cvlink{https://github.com/BU-DEPEND-Lab/SCUQ-RRG}{Code}}
\cvpub{Mammo-CLIP: A Vision Language Foundation Model to Enhance Data Efficiency and Robustness in Mammography}{\textbf{Shantanu Ghosh}, Clare B. Poynton, Shyam Visweswaran, Kayhan Batmanghelich}{International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI)}{2024. Early accept, top 11\%.}{\cvlink{https://shantanu-ai.github.io/projects/MICCAI-2024-Mammo-CLIP/}{Project} \cvlink{https://link.springer.com/chapter/10.1007/978-3-031-72390-2_59}{Paper} \cvlink{https://github.com/batmanlab/Mammo-CLIP}{Code}}
\cvpub{Distilling BlackBox to Interpretable models for Efficient Transfer Learning}{\textbf{Shantanu Ghosh}, Ke Yu, Kayhan Batmanghelich}{International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI)}{2023. Early accept, top 14\%.}{\cvlink{https://shantanu-ai.github.io/projects/MICCAI-2023-MoIE-CXR/}{Project} \cvlink{https://link.springer.com/chapter/10.1007/978-3-031-43895-0_59}{Paper} \cvlink{https://github.com/batmanlab/MICCAI-2023-Route-interpret-repeat-CXRs}{Code}}
\cvpub{Dividing and Conquering a BlackBox to a Mixture of Interpretable Models: Route, Interpret, Repeat}{\textbf{Shantanu Ghosh}, Ke Yu, Forough Arabshahi, Kayhan Batmanghelich}{International Conference on Machine Learning (ICML)}{2023.}{\cvlink{https://shantanu-ai.github.io/projects/ICML-2023-MoIE/}{Project} \cvlink{https://openreview.net/forum?id=0SgBUsL4W0}{Paper} \cvlink{https://github.com/batmanlab/ICML-2023-Route-interpret-repeat}{Code}}
\cvpub{DR-VIDAL: Doubly Robust Variational Information-theoretic Deep Adversarial Learning for Counterfactual Prediction and Treatment Effect Estimation}{\textbf{Shantanu Ghosh}, Zheng Feng, Jiang Bian, Kevin Butler, Mattia Prosperi}{American Medical Informatics Association (AMIA) Symposium}{2022. Oral presentation.}{\cvlink{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10148269/}{Paper} \cvlink{https://github.com/shantanu-ai/DR-VIDAL-AMIA-22}{Code}}
\cvpub{Anatomy-Guided Weakly-Supervised Abnormality Localization in Chest X-rays}{Ke Yu, \textbf{Shantanu Ghosh}, Zhexiong Liu, Christopher Deible, Kayhan Batmanghelich}{International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI)}{2022.}{\cvlink{https://arxiv.org/abs/2206.12704}{Paper} \cvlink{https://github.com/batmanlab/AGXNet}{Code}}
\cvpub{Causal AI with Real World Data: Do Statins Protect From Alzheimer's Disease Onset?}{Mattia Prosperi, \textbf{Shantanu Ghosh}, Zhaoyi Chen, Marco Salemi, Tianchen Lyu, Jiang Bian}{International Conference on Medical and Health Informatics (ICMHI)}{2021.}{}
\end{cvitems}

\cvsubsection{Journal Articles}
\begin{cvitems}
\cvpub{Anatomy-specific Progression Classification in Chest Radiographs via Weakly-Supervised Learning}{Ke Yu, \textbf{Shantanu Ghosh}, Zhexiong Liu, Clare Poynton, Christopher Deible, Kayhan Batmanghelich}{Radiology: Artificial Intelligence}{2024.}{\cvlink{https://pubs.rsna.org/doi/10.1148/ryai.230277}{Paper} \cvlink{https://github.com/batmanlab/SiameseAGXNet/tree/main}{Code}}
\cvpub{Propensity Score Synthetic Augmentation Matching using Generative Adversarial Networks}{\textbf{Shantanu Ghosh}, Christina Boucher, Jiang Bian, Mattia Prosperi}{Computer Methods and Programs in Biomedicine Update}{2021.}{\cvlink{https://www.sciencedirect.com/science/article/pii/S2666990021000197/}{Paper} \cvlink{https://github.com/shantanu-ai/PSSAM-GAN}{Code}}
\cvpub{Deep Propensity Network using a Sparse Autoencoder for Estimation of Treatment Effects}{\textbf{Shantanu Ghosh}, Jiang Bian, Yi Guo, Mattia Prosperi}{Journal of the American Medical Informatics Association}{2021.}{\cvlink{https://academic.oup.com/jamia/article-abstract/28/6/1197/6139936}{Paper} \cvlink{https://github.com/shantanu-ai/DPN-SA}{Code}}
\end{cvitems}

\cvsubsection{Peer-Reviewed Workshops}
\begin{cvitems}
\cvpub{Distributionally robust self-supervised learning for tabular data}{\textbf{Shantanu Ghosh}, Tiankang Xie, Mikhail Kuznetsov}{Table Representation Learning Workshop, NeurIPS}{2024.}{\cvlink{https://openreview.net/pdf?id=71u8OvjYbZ}{Paper} \cvlink{https://github.com/amazon-science/distributionally-robust-self-supervised-learning-for-tabular-data}{Code}}
\cvpub{Tackling Shortcut Learning in Deep Neural Networks: An Iterative Approach with Interpretable Models}{\textbf{Shantanu Ghosh}, Ke Yu, Forough Arabshahi, Kayhan Batmanghelich}{Workshop on Spurious Correlations, Invariance and Stability, ICML}{2023.}{\cvlink{https://arxiv.org/abs/2302.10289}{Paper}}
\cvpub{Bridging the Gap: From Post Hoc Explanations to Inherently Interpretable Models for Medical Imaging}{\textbf{Shantanu Ghosh}, Ke Yu, Forough Arabshahi, Kayhan Batmanghelich}{Workshop on Interpretable Machine Learning in Healthcare, ICML}{2023.}{\cvlink{https://openreview.net/pdf?id=sbOVNiSNY8}{Paper}}
\end{cvitems}

\cvsection{Teaching}
\begin{cvitems}
\item Medical Imaging With AI (EC 500), Boston University \sep Guest Lecturer \sep Fall 2025
\item Deep Learning (EC 523), Boston University \sep Teaching Assistant \sep Fall 2024
\item Introduction to Software Engineering (EC 327), Boston University \sep Teaching Assistant \sep Fall 2023
\end{cvitems}

\cvsection{Student Mentoring}
\begin{cvitems}
\item \href{https://www.linkedin.com/in/rayan-syed-507379296/}{Rayan Syed}, undergraduate student, Boston University \sep BU Outstanding Undergraduate Research Award.
\item \href{https://www.linkedin.com/in/aiden-wong-68962a22a/}{Ho Cheung Aiden Wong}, undergraduate student, Boston University \sep Next: M.S. Computer Science, Columbia University.
\item \href{https://www.linkedin.com/in/alexztang/}{Alex Tang}, undergraduate student, Dartmouth University.
\item \href{https://www.linkedin.com/in/ryan-gupta-a451b0262/}{Ryan Gupta}, undergraduate student, Boston University.
\item \href{https://www.linkedin.com/in/abhishek-varshney-a75748159/}{Abhishek Varshney}, master's student, Boston University \sep Next: Machine Learning Engineer, Poshmark.
\item \href{https://www.linkedin.com/in/akshatgurbuxani/}{Akshat Gurbuxani}, master's student, Boston University \sep Next: Software Engineer, Semiotic Labs.
\end{cvitems}

\cvsection{Academic Service}
\cvsubsection{Journal Reviewing}
Transactions on Machine Learning Research; IEEE Transactions on Medical Imaging; Journal of Biomedical Informatics; Medical Image Analysis; Journal of the American Medical Informatics Association; Computer Methods and Programs in Biomedicine; Biometrical Journal; Information Fusion.

\cvsubsection{Conference and Workshop Reviewing}
BMVC 2026; ECCV 2026; WACV 2025; ICCV 2025; ICML 2025; ICLR 2024--2026; AAAI 2024--2026; AISTATS 2025; NeurIPS 2023--2026; MICCAI 2024--2026; CVPR 2024--2026; CLeaR 2024--2025; GenAI4Health@NeurIPS 2024--2026; SCIS@ICML 2023; IMLH@ICML 2023.

\cvsection{Honors and Awards}
\begin{cvitems}
\item Full Travel Award, Symposium on Artificial Intelligence for Learning Health Systems (SAIL), 2026.
\item Outstanding Reviewer, NeurIPS, 2024.
\item Achievement Award, University of Florida graduate admission, 2019.
\item Star Employee Award, Cognizant Technology Solutions, Q4 2013 and Q4 2015.
\end{cvitems}

\cvsection{Talks and Abstract Presentations}
\begin{cvitems}
\item \textit{Text-Grounded Interpretability for Mammography Risk Prediction via Vision-Language Alignment}. SAIL 2026; International Breast Density and Cancer Risk Assessment Workshop, 2025.
\item \textit{A Domain-Specific Foundation Model Surpassing Generalist AI for Integrated Mammographic Diagnosis, Prognosis and Reporting}. Annual Boston Medical Imaging Workshop, MIT CSAIL, 2025.
\item \textit{Divide and Conquer: Carving Out Concept-based Models out of BlackBox for More Efficient Transfer Learning}. MedAI Group, Stanford University, 2024; ISP AI Forum, University of Pittsburgh, 2023.
\item \textit{DR-VIDAL for Counterfactual Prediction and Treatment Effect Estimation}. Oral talk, AMIA Annual Symposium, 2022.
\end{cvitems}

\cvsection{Technical Skills}
Python; PyTorch; TensorFlow; scikit-learn; C/C++; Java; C\#/.NET; JavaScript; HTML/CSS; Angular; Node.js; Oracle; MS SQL Server.

\end{document}
